---
title: "Gov 52 Replication Project"
author: "Daiana Lilo"
date: "5/07/2021"
output: pdf_document
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse) 
library(ggplot2)
library(arm)
library(stringr)
library(foreign)
library(Synth)
library(doBy)
library(rbounds)
library(rgenoud)
library(stargazer)
library(AER)
library(arm)
library(nnet)
library(reshape2)
```

## Introduction:

In the course Gov 52, students have become more exposed and familiarized with
statistical modeling, regression analysis, and data collection. In order to 
further extend my understanding of this material, I have decided to replicate
the work done in Jeffrey Harden's and Justin Kirkland's piece "Do Campaign
Donors Influence Polarization? Evidence from Public Financing in the American
States." On a base level, the piece attempts to answer the age-old question of
how money affects US politics and whether or not it is too influential.
Specifically, Harden and Kirkland (2016) looks at if the source of campaign 
funds, that is whether a campaign is funded privately or publicly, influences
legislative polarization. They consider the claim that private donors facilitate 
legislative polarization more than large-scale public donors. This is based on the 
assumption that individual and privatized donors are more ideologically extreme 
than the public as a whole. In order to study this, Harden and Kirkland use 
linear regressions and synthetic case studies to study the natural experiment in 
the New Jersey Assembly.

The replication code and appendix of this paper can be found at the following
link: *https://doi.org/10.7910/DVN/28868*



## Literature Review:

The topic of campaign finance and control has been one heavily discussed by both
the general public and political figures. The Supreme Court has heavily weighted in on 
the topic, first with the landmark case *Buckley v. Valeo*, where it was ruled
that limitations on certain types of election spending is unconstitutional and
money itself constitutes as protected speech under the First Amendment. More
recently in the 2010 case of *Citizens United v. Federal Election Commission*, 
the Court decided that the free speech clause in the First Amendment prohibits 
the United States government from restricting independent expenditures by
corporations. By making donations a form of legitimate political participation,
the Supreme Court furthered people's concerns about money in politics. Many 
studies have been conducted on this relationship between money and politics.
Gilens (2012) discusses the idea of democracy, and how such a system can be
achieved if a nation gives most political advantage to the richest members.
Meanwhile, Scholzman, Verba, and Brady (2012) looked at representation within
political participation, suggesting that the affluent and educated play the 
biggest role, potentially leading to political inequality. Furthermore, Hamm
and Hogan (2008) look at financing politics through a different lens, finding
that low contributions to a legislative campaign pave the way for a challenger
to face the incumbent. Finally, Stratmann and Aparicio-Castillo (2006) suggest
that restrictions on campaign financing can lead to closer margins of victory
in state legislative elections. We see with all these studies that the stakes
in studying finance in politics as a form of political action and participation
are extremely high, as landmark cases have been decided on this topic, and 
scholars continuously debate the influence of the action heavily.



## New Jersey Assembly Natural Experiment:

As aforementioned, Harden and Kirkland (2016) use a natural experiment found 
within the New Jersey Assembly to conduct their study. Specifically, the study
looks at the *New Jersey Fair and Clean Elections Pilot Project*, as the program
set forth public financing in the years 2005 and 2007 for some legislative 
Assembly members. The short experiment, which was not again renewed in 2009, 
allowed the authors to compare the voting behaviors of the New Jersey legislators
that were publicly funded and those who were not. Similar comparisons were done
with legislators in the states of Arizona and Maine, before and after the
implementation of public financing. While New Jersey implemented a pilot program
which introduced public financing, Arizona's and Maine's were on a state-wide 
scale. The laws were passed in 1998 and 1996 respectively in order to curb 
corruption. 



## Hypotheses: 

The study sets forth many theoretical expectations and hypotheses regarding
the question of campaign financing and legislative polarization. I will list a 
the hypotheses made in this study:

- Moderating Hypothesis: "(a) Committee Voting: Public financing of legislative elections reduces the 
ideological extremity of individual legislators’ voting behavior in committees."
"(b) Floor Voting: Public financing of legislative elections reduces the ideological 
extremity of individual legislators’ roll-call behavior on the floor of the chamber."


- The Flanking Hypothesis: "(a) Committee Voting: Public financing of legislative 
elections increases the ideological extremity of individual legislators’ voting 
behavior in committees."
"(b) Floor Voting: Public financing of legislative elections increases the 
ideological extremity of individual legislators’ roll-call behavior on the floor 
of the chamber."


- The Strategic Donor Hypothesis: "(a) Committee Voting: Public financing of 
legislative elections reduces the ideological extremity of individual legislators’ 
voting behavior in committees."
"(b) Floor Voting: Public financing of legislative elections exerts no effect on 
the ideological extremity of individual legislators’ roll-call behavior on the 
floor of the chamber."


- No-Strings-Attached Hypothesis: "(a) Committee Voting: Public financing of 
legislative elections exerts no effect on the ideological extremity of individual 
legislators’ voting behavior in committees."
"(b) Floor Voting: Public financing of legislative elections exerts no effect on 
the ideological extremity of individual legislators’ roll-call behavior on the 
floor of the chamber."



# Methodology:

As previously mentioned, the study primarily focuses on synthetic case studies 
to create counterfactuals in order to depict what happened in the states of 
New Jersey, Arizona, and Maine during events of both public and private financing. 
Limitations to this data exist, particularly the New Jersey curated information, 
as the data set is small. The objective of the study is to test the theories
mentioned above to estimate the causal effect of public financing on the 
legislative voting and polarization. Synthetic case control helps accomplish 
this, as it creates a mock "second version" of the event we are studying but
using controlled cases and variables only. This method of modeling is also
ideal for smaller data sample sets, such as the New Jersey example provides.

In order to create the models, roll-call data was utilized from the New Jersey
Legislative Assembly. Polarization, the variable of interest, is measured by
applying Martin Quinn Scores to the legislative votes. Below, we can see how 
synthetic case structures were developed and graphed (the names correspond to
specific assemblymen):

Please Note! The solid lines in the graphs present the extremity of each 
legislators ideal points and the dashed lines present synthetic case predictions 
before and after taking public financing.

Assembly Member 1
```{r}
# Loading Data One

assemb.comm <- read.dta("assemb-comm.dta")
assemb.comm$female <- ifelse(assemb.comm$Gender == "F", 1, 0)
assemb.comm$gop <- ifelse(assemb.comm$Party == "R", 1, 0)
treated <- c(71, 72, 82, 92, 141)
controls <- unique(assemb.comm$idnum[assemb.comm$PublicFinance == 0])
controls <- controls[-which(controls %in% treated)]
predictors <- c("variance", "Leader", "MoneyRaised", "Seniority", "Vote", "Race", "female", "gop", "Pres_DemShare_2000")

# Synthetic Case Control One

lrg.dp <- dataprep(assemb.comm, 
  predictors = predictors,
  predictors.op = "mean",
  time.predictors.prior = 1:3,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = 71,
  controls.identifier = controls,  
  time.optimize.ssr = 1:3,
  time.plot = 1:5)

# Generate synthetic 
lrg.synth <- synth(lrg.dp, method = "BFGS")
lrg.diag <- synth.tab(dataprep.res = lrg.dp, synth.res = lrg.synth)

lrg.pred <- lrg.dp$Y0plot %*% lrg.synth$solution.w 


par(mar = c(5, 5, .5, .5))
plot(1:5, lrg.dp$Y1plot, type = "n", ylim = c(0, 4.5), lwd = 2, xlab = "", ylab = "", axes = FALSE)
box(); grid()
abline(v = 4, lwd = 1)
lines(1:5, lrg.dp$Y1plot, lwd = 2)
lines(1:5, lrg.pred, lwd = 2, lty = 2)
axis(1, at = 1:5, labels = seq(2002, 2010, 2), cex.axis = 1.25)
axis(2, at = seq(0, 4.5, .5), cex.axis = 1.25, las = 2)
title(xlab = "Year", cex.lab = 1.5, line = 3)
title(ylab = "Extremity in Committee Vote Ideal Points", cex.lab = 1., line = 3)
legend("topleft", inset = .025, bty = "n", c("Linda R. Greenstein", "Synthetic Linda R. Greenstein"), lwd = 2, col = "black", lty = c(1, 2, -1), cex = 1.25)
text(2.25, .1, "First year after public financing", cex = 1.25)
arrows(3.3, .1, 3.95, .1, length = .1)
rug(assemb.comm$extremity, side = 2, ticksize = .025)
text(1.75, 1.4, bquote(paste("MSPE" == .(round(lrg.synth$loss.v, 5)))), cex = 1.25)

dev.off()
```

Assembly Member 2
```{r}

# Loading Data Two 

ldg.dp <- dataprep(assemb.comm, 
  predictors = predictors,
  predictors.op = "mean",
  time.predictors.prior = 1:2,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = 72,
  controls.identifier = controls,  
  time.optimize.ssr = 1:2,
  time.plot = 1:5)

# Generate synthetic Louis D. Greenwald 
ldg.synth <- synth(ldg.dp, method = "BFGS")
ldg.diag <- synth.tab(dataprep.res = ldg.dp, synth.res = ldg.synth)

# Plot LDG and S-LDG #
ldg.pred <- ldg.dp$Y0plot %*% ldg.synth$solution.w 

par(mar = c(5, 5, .5, .5))
plot(1:5, ldg.dp$Y1plot, type = "n", ylim = c(0, 4.5), lwd = 2, xlab = "", ylab = "", axes = FALSE)
box(); grid()
abline(v = 3, lwd = 1)
lines(1:5, ldg.dp$Y1plot, lwd = 2)
lines(1:5, ldg.pred, lwd = 2, lty = 2)
axis(1, at = 1:5, labels = seq(2002, 2010, 2), cex.axis = 1.25)
axis(2, at = seq(0, 4.5, .5), cex.axis = 1.25, las = 2)
title(xlab = "Year", cex.lab = 1.5, line = 3)
title(ylab = "Extremity in Committee Vote Ideal Points", cex.lab = 1, line = 3)
legend("topleft", inset = .025, bty = "n", c("Louis D. Greenwald", "Synthetic Louis D.", "Greenwald"), lwd = 2, col = "black", lty = c(1, 2, -1), cex = 1.25)
text(1.75, .25, "First year after", cex = 1.25)
text(1.75, .1, "public financing", cex = 1.25)
arrows(2.3, .25, 2.95, .25, length = .1)
rug(assemb.comm$extremity, side = 2, ticksize = .025)
text(1.75, 1.55, bquote(paste("MSPE" == .(round(ldg.synth$loss.v, 5)))), cex = 1.25)

dev.off()

```

Assembly Member 3
```{r}

# Loading Data Three

gmj.dp <- dataprep(assemb.comm, 
  predictors = predictors,
  predictors.op = "mean",
  time.predictors.prior = 1:3,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = 82,
  controls.identifier = controls,  
  time.optimize.ssr = 1:3,
  time.plot = 1:5)

# Generate synthetic Gordon M. Johnson #
gmj.synth <- synth(gmj.dp, method = "BFGS")
gmj.diag <- synth.tab(dataprep.res = gmj.dp, synth.res = gmj.synth)

# Plot GMJ and S-GMJ #
gmj.pred <- gmj.dp$Y0plot %*% gmj.synth$solution.w 

par(mar = c(5, 5, .5, .5))
plot(1:5, gmj.dp$Y1plot, type = "n", ylim = c(0, 4.5), lwd = 2, xlab = "", ylab = "", axes = FALSE)
box(); grid()
abline(v = 4, lwd = 1)
lines(1:5, gmj.dp$Y1plot, lwd = 2)
lines(1:5, gmj.pred, lwd = 2, lty = 2)
axis(1, at = 1:5, labels = seq(2002, 2010, 2), cex.axis = 1.25)
axis(2, at = seq(0, 4.5, .5), cex.axis = 1.25, las = 2)
title(xlab = "Year", cex.lab = 1.5, line = 3)
title(ylab = "Extremity in Committee Vote Ideal Points", cex.lab = 1, line = 3)
legend("topleft", inset = .025, bty = "n", c("Gordon M. Johnson", "Synthetic Gordon M. Johnson"), lwd = 2, col = "black", lty = c(1, 2, -1), cex = 1.25)
text(2.25, .1, "First year after public financing", cex = 1.25)
arrows(3.3, .1, 3.95, .1, length = .1)
rug(assemb.comm$extremity, side = 2, ticksize = .025)
text(1.75, 1.4, bquote(paste("MSPE" == .(round(gmj.synth$loss.v, 5)))), cex = 1.25)

dev.off()

```

Assembly Member 4
```{r}

# Loading Data Three

sdt.dp <- dataprep(assemb.comm, 
  predictors = predictors,
  predictors.op = "mean",
  time.predictors.prior = 1:2,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = 141,
  controls.identifier = controls,  
  time.optimize.ssr = 1:2,
  time.plot = 1:5)

# Generate synthetic Samuel D. Thompson #
sdt.synth <- synth(sdt.dp, method = "BFGS")
sdt.diag <- synth.tab(dataprep.res = sdt.dp, synth.res = sdt.synth)

# Plot SDT and S-SDT #
sdt.pred <- sdt.dp$Y0plot %*% sdt.synth$solution.w 

par(mar = c(5, 5, .5, .5))
plot(1:5, sdt.dp$Y1plot, type = "n", ylim = c(0, 4.5), lwd = 2, xlab = "", ylab = "", axes = FALSE)
box(); grid()
abline(v = 3, lwd = 1)
lines(1:5, sdt.dp$Y1plot, lwd = 2)
lines(1:5, sdt.pred, lwd = 2, lty = 2)
axis(1, at = 1:5, labels = seq(2002, 2010, 2), cex.axis = 1.25)
axis(2, at = seq(0, 4.5, .5), cex.axis = 1.25, las = 2)
title(xlab = "Year", cex.lab = 1.5, line = 3)
title(ylab = "Extremity in Committee Vote Ideal Points", cex.lab = 1, line = 3)
legend("topleft", inset = .025, bty = "n", c("Samuel D. Thompson", "Synthetic Samuel D.", "Thompson"), lwd = 2, col = "black", lty = c(1, 2, -1), cex = 1.25)
text(1.75, .25, "First year after", cex = 1.25)
text(1.75, .1, "public financing", cex = 1.25)
arrows(2.3, .25, 2.95, .25, length = .1)
rug(assemb.comm$extremity, side = 2, ticksize = .025)
text(1.85, 1.55, bquote(paste("MSPE" == .(round(sdt.synth$loss.v, 5)))), cex = 1.25)

dev.off()

```



# Be warned! This will take a longer time to run, as we are filling in the gaps
of many synthetic case tests in order to see the differentiation of ideal points.
```{r}

# Combination of Assemblymen

predictors2 <- predictors[-2] # For controls == 1 (John M. Bramnick)

gaps <- matrix(nrow = length(controls), ncol = 5)
mspe.ratios <- numeric(length(controls))
bad.fit <- numeric(22)
for(i in 1:22){
if(i == 1){
placebo.dp <- dataprep(assemb.comm, 
  predictors = predictors2,
  predictors.op = "mean",
  time.predictors.prior = 1:2,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = controls[i],
  controls.identifier = controls[-i],  
  time.optimize.ssr = 1:2,
  time.plot = 1:5)
} else
placebo.dp <- dataprep(assemb.comm, 
  predictors = predictors,
  predictors.op = "mean",
  time.predictors.prior = 1:2,
  dependent = "extremity",
  unit.variable = "idnum",
  unit.names.variable = "Name",
  time.variable = "timenum",
  treatment.identifier = controls[i],
  controls.identifier = controls[-i],  
  time.optimize.ssr = 1:2,
  time.plot = 1:5)
  
placebo.synth <- synth(placebo.dp, method = "BFGS")
placebo.pred <- placebo.dp$Y0plot %*% placebo.synth$solution.w
gaps[i, ] <- placebo.dp$Y1plot - placebo.pred 
mspe.ratios[i] <- mean((placebo.dp$Y1plot[3:5] - placebo.pred[3:5])^2)/mean((placebo.dp$Y1plot[1:2] - placebo.pred[1:2])^2)
bad.fit[i] <- as.numeric(ifelse(placebo.synth$loss.v > sdt.synth$loss.v*5, 1, 0))
print(i)
}

# Treated legislator gaps #
lrg.gaps <- lrg.dp$Y1plot - (lrg.dp$Y0plot %*% lrg.synth$solution.w) 
ldg.gaps <- ldg.dp$Y1plot - (ldg.dp$Y0plot %*% ldg.synth$solution.w) 
gmj.gaps <- gmj.dp$Y1plot - (gmj.dp$Y0plot %*% gmj.synth$solution.w) 
sdt.gaps <- sdt.dp$Y1plot - (sdt.dp$Y0plot %*% sdt.synth$solution.w) 

# Treated legislator MSPE ratios #
lrg.ratio <- mean((lrg.dp$Y1plot[4:5] - lrg.pred[4:5])^2)/mean((lrg.dp$Y1plot[1:3] - lrg.pred[1:3])^2)
ldg.ratio <- mean((ldg.dp$Y1plot[3:5] - ldg.pred[3:5])^2)/mean((ldg.dp$Y1plot[1:2] - ldg.pred[1:2])^2)
gmj.ratio <- mean((gmj.dp$Y1plot[4:5] - gmj.pred[4:5])^2)/mean((gmj.dp$Y1plot[1:3] - gmj.pred[1:3])^2)
sdt.ratio <- mean((sdt.dp$Y1plot[3:5] - sdt.pred[3:5])^2)/mean((sdt.dp$Y1plot[1:2] - sdt.pred[1:2])^2)

# Treated legislator permutation p-values #
lrg.p <- length(which(mspe.ratios >= lrg.ratio))/(length(controls) + 4)
ldg.p <- length(which(mspe.ratios >= ldg.ratio))/(length(controls) + 4)
gmj.p <- length(which(mspe.ratios >= gmj.ratio))/(length(controls) + 4)
sdt.p <- length(which(mspe.ratios >= sdt.ratio))/(length(controls) + 4)

par(mar = c(5, 5, .5, .5))
plot(1:5, ldg.gaps, type = "n", ylim = c(-1.5, 1.5), lwd = 2, xlab = "", ylab = "", axes = FALSE) 
box(); grid()
for(i in 1:22){
if(bad.fit[i] == 0){
lines(1:5, gaps[i, ], type = "l", col = "gray80", lwd = 2)
} else cat("bad fit", "\n")
} 
abline(h = 0, lwd = 1)
abline(v = 3, lwd = 1)
lines(1:5, ldg.gaps, lwd = 2, lty = 1)
lines(1:5, sdt.gaps, lwd = 2, lty = 2)
lines(1:5, lrg.gaps, lwd = 2, lty = 3)
lines(1:5, gmj.gaps, lwd = 2, lty = 4)
axis(1, at = 1:5, labels = seq(2002, 2010, 2), cex.axis = 1.25)
axis(2, at = seq(-1.5, 1.5, .5), cex.axis = 1.25, las = 2)
title(xlab = "Year", cex.lab = 1.5, line = 3)
title(ylab = "Difference in Extremity from Synthetic Legislator", cex.lab = 1, line = 3)
legend("topleft", inset = .025, ncol = 2, bty = "n", c("Louis D. Greenwald", "Samuel D. Thompson", "Linda R. Greenstein", "Gordon M. Johnson", "Placebo Legislators"), lwd = 2, lty = c(1, 2, 3, 4, 1), col = c(rep("black", times = 4), "gray80"), cex = 1)
text(1.75, -1.125, "First year after", cex = 1)
text(1.75, -1.25, "public financing", cex = 1)
arrows(2.3, -1.125, 2.95, -1.125, length = .1)

dev.off()

```

The above synthetic case study focuses on New Jersey Legislative Assemblymen,
depicting that voting patterns do not change significantly whether an 
assembly man is either publicly or privately financed. Black lines represent 
legislators who took public financing and gray lines represent control legislators 
who did not participate.



## Lm regressions


We also see the use of linear regression statistical modeling in state-wide use 
of legislative financing comparison:

New Jersey Legislative Assembly modeling:

```{r results = "asis", warning = FALSE, message= FALSE}

### Floor Votes ###
assemb.floor <- read.dta("assemb-floor.dta")
assemb.floor$female <- ifelse(assemb.floor$Gender == "F", 1, 0)
assemb.floor$gop <- ifelse(assemb.floor$Party == "R", 1, 0)
treated <- c(67, 68, 78, 89, 136)
controls <- unique(assemb.floor$idnum[assemb.floor$PublicFinance == 0])
controls <- controls[-which(controls %in% treated)]
predictors <- c("variance", "Leader", "MoneyRaised", "Seniority", "Vote", "Race", "female", "gop", "Pres_DemShare_2000")

assemb.floor$post.treat <- ifelse(assemb.floor$timenum > 3, 1, 0)
assemb.floor$treated <- ifelse(assemb.floor$idnum %in% treated, 1, 0)

floor.did <- lm(extremity ~ variance + Leader + MoneyRaised + Seniority + Vote + Race + female + gop + Pres_DemShare_2000 + post.treat + treated + post.treat*treated, data = assemb.floor)

stargazer(floor.did)

round(coef(floor.did), 3)
round(confint(floor.did)["post.treat:treated", ], 3)
round(range(assemb.floor$extremity), 3)
round(confint(floor.did)["post.treat:treated", ], 3)[2]/sd(assemb.floor$extremity)

### Committee Votes ###
assemb.comm <- read.dta("assemb-comm.dta")
assemb.comm$female <- ifelse(assemb.comm$Gender == "F", 1, 0)
assemb.comm$gop <- ifelse(assemb.comm$Party == "R", 1, 0)
treated <- c(71, 72, 82, 92, 141)
controls <- unique(assemb.comm$idnum[assemb.comm$PublicFinance == 0])
controls <- controls[-which(controls %in% treated)]
predictors <- c("variance", "Leader", "MoneyRaised", "Seniority", "Vote", "Race", "female", "gop", "Pres_DemShare_2000")

assemb.comm$post.treat <- ifelse(assemb.comm$timenum > 3, 1, 0)
assemb.comm$treated <- ifelse(assemb.comm$idnum %in% treated, 1, 0)

comm.did <- lm(extremity ~ variance + Leader + MoneyRaised + Seniority + Vote + Race + female + gop + Pres_DemShare_2000 + post.treat + treated + post.treat*treated, data = assemb.comm)

stargazer(comm.did)

round(coef(comm.did), 3)
round(confint(comm.did)["post.treat:treated", ], 3)
round(range(assemb.comm$extremity), 3)
round(confint(comm.did)["post.treat:treated", ], 3)[2]/sd(assemb.comm$extremity)

```

# Public Financing and the Electoral Connection Between Private Donors and Legislators 

The linear regressions show the importance of polarization and how each legislator
votes. We see here that there is not much of a difference between a legislator
that was funded publicly and privately. Voting remains the same, and coefficient
estimates in change do not prove to be statistically significant.

```{r results = "asis", warning = FALSE, message= FALSE}

# Note! Formatting of the stargazer tables caused tabled to break even more than
# they already appear to be broken. I assume it is because the tables use such
# a wide array of predictors that they end up being longer than the page? But
# Le said this was okay!

stmed <- read.dta("state-diff-medians.dta")
clp.states <- c("AZ", "CA", "CO", "CT", "DE", "FL", "KS", "KY", "ME", "MD", "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "OK", "OR", "PA", "RI", "SD", "UT", "WV", "WY")
west <- c("WA", "OR", "CA", "ID", "NV", "AZ", "UT", "WY", "MT", "CO", "NM")
mwest <- c("ND", "SD", "NE", "KS", "OK", "MO", "IA", "MN", "WI", "IL", "IN", "MI", "OH")
south <- c("TX", "LA", "AR", "TN", "KY", "AL", "GA", "FL", "SC", "NC", "VA", "WV")

stmed$clp <- ifelse(stmed$state %in% clp.states, 1, 0) 
stmed$west <- ifelse(stmed$state %in% west, 1, 0) 
stmed$mwest <- ifelse(stmed$state %in% mwest, 1, 0) 
stmed$south <- ifelse(stmed$state %in% south, 1, 0) 
stmed <- stmed[ , c("state", "year", "alpha", "pm", "avgdist", "ideology", "ideoex", "dividedgov", "gopshare", "deficit", "squire_score", "income", "unemployment", "population", "populationdensity", "grants", "gsp", "termlimits_house", "termlimits_senate", "demcontrol", "clp", "govideo2", "west", "mwest", "south")]

## Impute missing difference in party median and average distance values ##
pm.mi <- lm(pm ~ ideology + ideoex + dividedgov + gopshare + deficit + squire_score + income + unemployment + population + populationdensity + grants + gsp + termlimits_house + termlimits_senate + demcontrol + clp + govideo2 + west + mwest + south, data = stmed)

stargazer(pm.mi)

ad.mi <- lm(avgdist ~ ideology + ideoex + dividedgov + gopshare + deficit + squire_score + income + unemployment + population + populationdensity + grants + gsp + termlimits_house + termlimits_senate + demcontrol + clp + govideo2 + west + mwest + south, data = stmed)

stargazer(ad.mi)

dm <- stmed[ , -c(1:5)]
stmed$pm2 <- as.matrix(cbind(1, dm)) %*% coef(pm.mi)
stmed$pm3 <- ifelse(is.na(stmed$pm) == TRUE, stmed$pm2, stmed$pm)

stmed$ad2 <- as.matrix(cbind(1, dm)) %*% coef(ad.mi)
stmed$ad3 <- ifelse(is.na(stmed$avgdist) == TRUE, stmed$ad2, stmed$avgdist)

stmed$post.treat <- ifelse(stmed$year > 2000, 1, 0)
stmed$treated <- ifelse(stmed$alpha %in% c(3, 19), 1, 0)

st.did <- lm(pm3 ~ ideology + ideoex + dividedgov + gopshare + deficit + squire_score + income + unemployment + population + populationdensity + grants + gsp + termlimits_house + termlimits_senate + demcontrol + clp + govideo2 + west + mwest + south + post.treat + treated + post.treat*treated, data = stmed)

stargazer(st.did)

round(coef(st.did), 3)
round(confint(st.did)["post.treat:treated", ], 3)
round(range(stmed$pm3), 3)
round(confint(st.did)["post.treat:treated", ], 3)[2]/sd(stmed$pm3)

```



## Findings: 

Both the synthetic case studies and the linear regression models above provide 
evidence that public financing has a very insignificant effect on legislative 
voting behavior. Evidence above actually shows that legislators basically vote 
the same whether they are publicly or privately funding, suggesting that 
campaign finance does not heavily affect legislative polarization. Therefore, 
the authors discover that although campaign finance remains a volatile expression
of political freedom and expression, it does not constitute as a significant 
influence in the polarization of individual legislators or legislative parties. 
Voting is not significantly changed by private donations, most likely due to the 
assumption that a return is not expected during the time of a donation, and instead,
private donors already focus on representing the legislators they already know
they will agree with, rather than attempt to influence ones they do not.



## Project Expansion:


There is many ways this project could be expanded. First, it was acknowledged
that limitations in data collection exist, as the data set is extremely narrow.
Further data collection and a differences and differences approach using states
with publicly funded legislative offices could provide more concrete evidence 
to the findings of Harden and Kirkland (2016). There is much left to be explored 
and extended content-wise within this study as well. Yes, it is determined that 
public financing has no effect on voting behavior, but there could be many other
notable effects. It could influence other parts of the legislative-decision
making process, such as bill authoring lobbying, that were not focused upon in
this study. A written extension of this paper could be expanded in such manner.


As for an expansion on this particular study, one can go beyond a linear regression
model and run other types of models to see other effects of public financing and
voting. Below, I take models previously done above in the study, specifically 
the ones focusing on New Jersey floor roll calls, and run a quasi-poisson model
to look for over-dispersion. I then run Chi Square tests to test for such 
over-dispersion (code in .Rmd file).


```{r}

# First model plugged into quasi-poisson:

quasi.floor.did <- glm(extremity ~ variance + Leader + MoneyRaised + Seniority + 
                       Vote + Race + female + gop + Pres_DemShare_2000 + 
                       post.treat + treated + post.treat*treated, 
                       family = quasipoisson, data = assemb.floor)

summary(quasi.floor.did)

stargazer(quasi.floor.did)

# Over-dispersion

prediction <- predict(quasi.floor.did, type = "response")

predictionratio <- (assemb.floor$extremity - prediction)/sqrt(prediction)

sum(predictionratio^2)/(length(assemb.floor$extremity) - 13)


# Chi Square Tests

1 - pchisq(summary(quasi.floor.did)$deviance, summary(quasi.floor.did)$df.residual)

pchisq(47.86 - 13.522, 263 - 251, lower = FALSE)

```

Due to our low values, we see that the model is still a good fit for the data,
even though over-dispersion does exist slightly. 


## Conclusion:

In this project, I walked through the study and analysis done in the piece
Harden and Kirkland (2016): "Do Campaign Donors Influence Polarization? Evidence 
from Public Financing in the American States," which looked at the effects of
public financing on legislative polarization. I walked through the synthetic
case study used to determine this answer, as well as the linear regression
models that sought to discover a connection between voting patterns in the
Legislative and public financing. I replicated the models accurately showcasing
the viewer of this project the analysis conducted. I also put the statistic
results of the linear regression models into stargazer table, allowing them to be
understood and interpreted easier for the viewer. Contrary to popular general 
belief, the authors provide evidence that campaign funding has minimal influence on 
polarization. After replication of the figures and tables, I ultimately agree with
these outcomes, as I was able to reproduce the same results. 

Finally, I expanded upon this paper qualitatively, discussing further steps one 
could take in data collection and expansion in studying the effects of campaign 
finance on the decision-making structure of legislatures in the United States.
Quantitatively, I also included a quasi-poisson model in order to account for
over-dispersion in the data, and conducted a Chi-Square test on this. I was able
to determine that the data does fit the model properly, an important note of this
study. 

I would like to thank Jeffrey Harden and Justin Kirkland for making their data
readily available for public use, as this allows students and researchers to 
properly replicate their work and fully understand their findings. I would 
also like to thank Professor Jeff Gill and Le Bao for their work this semester,
as this course has become fundamental to my understanding of statistical modeling,
and an essential component of my future in data science. 


## Citations:

Gilens, Martin. Affluence and Influence: Economic Inequality and Political Power 
in America. PRINCETON; OXFORD: Princeton University Press, 2012. 
doi:10.2307/j.ctt7s1jn.

Hamm, Keith E, and Hogan, Robert E. "Campaign Finance Laws and Decisions in 
State Legislative Candidacy Elections." Political Research Quarterly 61, 
no. 3 (2008): 458-67.

Harden, Jeffrey J., and Justin H. Kirkland. "Do Campaign Donors Influence 
Polarization? Evidence from Public Financing in the American States." 
Legislative Studies Quarterly 41, no. 1 (2016): 119-52. doi:10.1111/lsq.12108.

Schlozman, Kay Lehman, Verba, Sidney, and Brady, Henry E. The Unheavenly Chorus. 
Princeton: Princeton University Press, 2012.

Thomas Stratmann, and Francisco J. Aparicio-Castillo. "Competition Policy for 
Elections: Do Campaign Contribution Limits Matter?" 
Public Choice 127, no. 1/2 (2006): 177-206.


Link to my Github with all of the Rmd code and associated files:
**https://github.com/daililo/ReplicationProject.git**
